Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-04-13 ThesisJP/Introduction/introduction.tex
Added paper 1.

\subsection{Paper\,I}
\textbf{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}\\
J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng\\
{\it IEEE Transactions on Oceanic Engineering, accepted for publication.}\\\\
The first paper describes in detail how the Capon beamformer is mapped to the GPU architecture. Even though the paper is written within the field of active \nom{sonar}{SOund Navigation And Ranging (usually under water)} imaging, the depicted implementation is applicable to a vast range of active imaging systems. A similar discussion for cardiac ultrasound imaging can be found in \textbf{Paper\,VI}.  Active sonar imaging typically differs from medical ultrasound imaging by a lower real-time requirement and fewer array elements. This makes it somewhat easier to reach the goal of real-time processing.

>>>>

\subsection{Paper\,I}
\textbf{An Optimized GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}\\
J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng\\
{\it IEEE Transactions on Oceanic Engineering, accepted for publication.}\\\\
The first paper describes in detail how the Capon beamformer is mapped to the GPU architecture. Even though the paper is written within the field of active \nom{sonar}{SOund Navigation And Ranging (usually under water)} imaging, the depicted implementation is applicable to a vast range of active imaging systems. A similar discussion for cardiac ultrasound imaging can be found in \textbf{Paper\,VI}.  Active sonar imaging typically differs from medical ultrasound imaging by a lower real-time requirement and fewer array elements. This makes it somewhat easier to reach the goal of real-time processing.

### 2014-04-13 ThesisJP/Thesis.tex
Added paper 1.

@@

I would like to thank my family for all support. But most of all, I want to thank Beate for all her love, patient and support. Without it I would never have manage to complete this theses.
\null
\vfill
\hfill Dedicated to Sofie Mathilde \AA{}sen
\CustChapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}

This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, accepted for publication}.
	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. 76-85, Jan 2014}.
 	\item \textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, accepted for publication}.
	\item \textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012, vol. 8320, pp. 832008}.
	\item \textbf{J.\:P.\:\AA{}sen} and S.\:Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012, pp. 1643-1646}.
\end{enumerate}

@@

%%%% Paper 1 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{GPU MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	\textbf{Jon Petter \AA{}sen}$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{IEEE Transactions on Oceanic Engineering, accepted for publication}.
%\newpage\input{./CaponSonarGPU/CaponSonarGPU}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./CaponSonarGPU/bibCaponSonarGPU]
\end{bibunit}

>>>>

% from Paper 1
\usepackage{colortbl}
\usepackage{appendix}

@@

I would like to thank my family and all my friends for all support. But most of all, I want to thank Beate for all her love, patient and support. Without it I would never have manage to complete this theses.
\null
\vfill
\hfill To: Sofie Mathilde \AA{}sen
\CustChapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}

This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "An optimized GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, accepted for publication}.
	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. 76-85, Jan 2014}.
 	\item \textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, accepted for publication}.
	\item \textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012, vol. 8320, pp. 832008}.
	\item \textbf{J.\:P.\:\AA{}sen} and S.\:Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012, pp. 1643-1646}.
\end{enumerate}

@@

%%%% Paper 1 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{An Optimized GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{GPU MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	\textbf{Jon Petter \AA{}sen}$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{IEEE Transactions on Oceanic Engineering, accepted for publication}.
\newpage
{
\input{./Paper1/howto_howto_capon}
}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Paper1/library]
\end{bibunit}
